Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

>>>>

Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.  Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.  This relationship can be seen in the following regression output table.  This regression output was generated using a simple least square regression model.

```{r echo = FALSE, cache= FALSE, include= FALSE}

# Library Zelig (can be buggy if loaded too early)
library(Zelig)

# Library Amelia for imputed data
library(Amelia)

# Import df of dependent and independent variables
CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")

############ Running a regression with full df (including omitted variables)
RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
```

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

# Create vector of lables
labels_1 <- c('Way of Teaching', 'Perceived Capabilities', 'Fear of Failure', 'Perceived Good Opportunities', 
             'Fear of Failure x Perceived Good Opportunities')

dlabels_1 <- c('Entrepreneurial Intention', 'Nascent Entrepreneur', 'Entrepreneurship Owner')

# Regression output table with country-specific effects
stargazer::stargazer(RG1, RG2, RG3,
                     title = 'Linear Regression Estimates with Country-specific Effects',
                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)

To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.  Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.  A regression output table with these results has been included below.

# Run three regression equations again (omitting country-specific effects)
RG4 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG5 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

RG6 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)

<br>
```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

# Regression output table with country-specific effects
stargazer::stargazer(RG4, RG5, RG6,
                     title = 'Linear Regression Estimates omitting Country-specific Effects',
                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)

Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.   Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.  This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).  Equation  titled "Imputed" were calculated using this imputed data frame.

To generate the simulations, we decided to use the R package Zelig.  This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).  We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.  A regression output table and our simulation results are included below.  Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."

############ Running a regression omitting omitted variables

# Generate a df omitting omitted variables
CD_omitted <- na.omit(CD)

# Run a least squares regression with Zelig
Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")

############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables

# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)

# Omit variables that could not be imputed by Adelia (b/c of lack of data)
CI_omitted <- na.omit(CI)

# Regression equation with imputed values
Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")

############ Set range of values for Z1 and Z2 using imputed and not imputed dfs

####### Simulate Percent Perceived

# Set range of PercentPerceived values in simulation (NOT IMPUTED)
x.out1 <- setx(Z1, PercentPerceived = 9:67)

# Run simulation (default 1000 trials) (NOT IMPUTED)
simz1 <- sim(Z1, x = x.out1)

# Set range of PercentPerceived values in siumlation (IMPUTED)
x.out2 <- setx(Z2, PercentPerceived = 9:67)

# Run simulation (default 1000 trials) (IMPUTED)
simz2 <- sim(Z2, x = x.out2)

####### Simulate Way of Teaching

# Set range of WayofTeaching values in simulation (NOT IMPUTED)
x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)

# Run simulation (default 1000 trials) (NOT IMPUTED)
simz3 <- sim(Z1, x = x.out3)

# Set range of WayofTeaching values in simulation (IMPUTED)
x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)

# Run simulation (default 1000 trials) (IMPUTED)
simz4 <- sim(Z2, x = x.out4)

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}

# Set new vector for dependent variable label
dlabels_2 <- c('Entrepreneurship Owner')

# Regression output table with country-specific effects
stargazer::stargazer(Z1, Z2,
                     title = 'Linear Regression Estimates omitting Country-specific Effects',
                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
                     font.size =  "small", type = 'latex', no.space = TRUE,
                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
```

```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
library("Zelig")

# Set layout
par(mfrow = c(2, 2))

# Plot simz1 (unimputed)
plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
     main = "Unimputed (Equation 1)")

# Plot simz2 (imputed)
plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
     main = "Imputed (Equation 2)")

# Plot simz3 (unimputed)
plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
     main = "Unimputed (Equation 1)")

# Plot simz4 (imputed)
plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
     main = "Imputed (Equation 2)")

**Results**

**Limitations of the data**

From the results and from the description of the data made earlier, one can easily foresee quite a few limitations to the consistency and effectiveness of the data we used for this research. Although they are obvious, one should still name them here.

The GEM National Expert Survey however interesting and innovative for its extensive look into new sorts of data still allows for much improvement. It is essentially supposed to help control for the environmental determinants of entrepreneurship, which are here called the framework conditions. The major issue is not so much what it aims at revealing of the entrepreneurial context of each country but it has much more to do with methodology of data collection. Indeed, for each of these framework conditions, only four experts answered the survey, which makes the measure be very dependent on the individual respondent. This leads to highly variant data.

Regarding the D01 indicator we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect. Indeed, as we look at the way of teaching and education features, these are generally
